### 2022-08-09 main/chapter_2ljets.tex
add dataset info; begin typing discussion

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lcccccc}
& \multicolumn{2}{c}{Fitted}
& Data
& $A\epsilon\sigma_{\mathrm{obs}}^{95}~\mathrm{fb}$
& $S_{\mathrm{obs}}^{95}$
& $S_{\mathrm{exp}}^{95}$
& $\clb$
& $p_{s\!=\!0}$
\\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & $21$ & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$
\\[.5ex]
DR-Low & $22$ & $4$ & $18$ & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$
\\[.5ex]
DR-Int & $35$ & $4$ & $38$ & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$
\\[.5ex]
DR-High & $3.9$ & $0.5$ & $0$ & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0$ & $0.50$
\\[.5ex]
DR-$\llbb$ & $0.51$ & $0.20$ & $0$ & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$
\\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\cls$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\clb$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test
statistic~\cite{Cowan:2010js}.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided
test.
All $p$-values are estimated by simulation of alternative data.
Values with errors are rounded to one or two significant figures according
the the PDG rounding scheme~\cite{pdg2020review}.
}
\label{tab:2ljets_discovery}
\end{table}

@@

\section{Events}
\label{sec:2ljets_events}
\TODO{make sure we say 136ifb from 2015 to 2018 run 2 data. Good run lists etc}

This section describes the events selected for the $\twoljets$ searches, the
reconstructed particle objects derived from those events and various
important event variables.

@@

Triggers and object definitions are shared between the three $\twoljets$
searches.
Higher level event variables and selections will only be described for the
$\twoljets$-electroweak search.

@@

It is certainly arguable that the pathological test statistic distributions
observed in DR-Low indicate a bug that should be fixed.
However, the statistical software packages that generated this result
--- \roofit\ through \histfitter ---
define in silicon the standard statistical methods for \atlas\ SUSY searches.
To diverge from them would make our result incomparable.
What they do defines what is correct.
All \pyhf\ can do is imitate.
There is no such thing as a bug.

@@

\TODO{}

>>>>

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lcccccc}
& \multicolumn{2}{c}{Fitted}
& Data
& $A\epsilon\sigma_{\mathrm{obs}}^{95}\,\mathrm{fb}$
& $S_{\mathrm{obs}}^{95}$
& $S_{\mathrm{exp}}^{95}$
& $\clb$
& $p_{s\!=\!0}$
\\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & $21$ & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$
\\[.5ex]
DR-Low & $22$ & $4$ & $18$ & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$
\\[.5ex]
DR-Int & $35$ & $4$ & $38$ & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$
\\[.5ex]
DR-High & $3.9$ & $0.5$ & $0$ & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0$ & $0.50$
\\[.5ex]
DR-$\llbb$ & $0.51$ & $0.20$ & $0$ & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$
\\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\cls$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\clb$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test
statistic~\cite{Cowan:2010js}.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided
test.
All $p$-values are estimated by simulation of alternative data.
Values with errors are rounded to one or two significant figures according
the the PDG rounding scheme~\cite{pdg2020review}.
}
\label{tab:2ljets_discovery}
\end{table}

@@

\section{Events}
\label{sec:2ljets_events}
This section describes the events selected for the $\twoljets$ searches, the
reconstructed particle objects derived from those events and various
important event variables.

@@

Our dataset comprises $136.0\,\mathrm{fb}^{-1}$ ($\pm 1.7\%$) of integrated
luminosity observed during normal operations of the \atlas\ detector in the
years $2015$ through to $2018$ of the LHC Run~2~\cite{DAPR-2018-01}.
Triggers and object definitions are shared between the three $\twoljets$
searches.
Higher level event variables and selections will only be described for the
$\twoljets$-electroweak search.

@@

It is certainly arguable that the pathological test statistic distributions
observed in DR-Low indicate a bug that should be fixed.
However, the statistical software packages that generated this result
--- \roofit\ through \histfitter\ ---
define in silicon the standard statistical methods for \atlas\ SUSY searches.
To diverge from them would make our result incomparable.
What they do defines what is correct.
All \pyhf\ can do is imitate.
There is no such thing as a bug.

@@

From \atlas' large and valuable Run~2 dataset, our $\twoljets$ searches
have extracted a sharper image of the high energy processes that simultaneously
produce leptons, jets and missing transverse momentum in proton-proton
collisions at the Large Hadron Collider.
The core message is clear: we see no indication of any additive process
atop the Standard Model.

These searches do not exist in isolation. They extend and strengthen the
results of numerous previous \atlas\ searches that have used similar or smaller
datasets and found similar conclusions.
By providing refined and updated interpretations, we have advanced \atlas' SUSY
research programme in this $2\ell$+jets+$\met$ channel.
My focus has been on the $\twoljets$-electroweak search within this project.
Its result is a central pillar of the visible effects of both C1N2 and GMSB
simplified supersymmetric models, and uniquely contributes exclusion
(under the $95\%$ $\cls$ prescription) of certain regions of the models'
parameter spaces.

% model (in)dependent
Although designed to study potential supersymmetric effects, the results
themselves are open to wider interpretation.
Serialized \heplikelihood\ models and region definitions that we publish
through the paper~\cite{atlas2022searches} and its \hepdata\
archive~\cite{hepdata.116034} are resources that remain useful for
reinterpretation in future research testing different physical hypotheses
--- both of the orthogonal multi-bin selections designed for model-dependent
sensitivity and through our model-independent discovery regions.

% limitations
% overly ambitious design
% lack: resources to study, methods to analyse
% cost: delays, opportunity cost
% higher quality result by simpler more robust design published sooner
% accelerate science by doing it now, not in two years.
